A general and efficient representation of ancestral recombination graphs

### 2024-04-22 response-to-reviewers.tex

\subsection*{Specific comments}
% We address your specific comments below:
% % \reviewersection

\section*{Response to the reviewers}
% General intro text goes here
We thank the reviewers for their close reading of our manuscript and
insightful comments. In the following we address the points raised
in turn.

% Let's start point-by-point with Reviewer 1
\reviewersection

\begin{point}
In this article, Wong et al. describe a data structure called the ``genome
ARG''
(gARG), designed to effectively represent information in ancestral
recombination graphs. The authors have done an excellent job of clearly
explaining the concept and offering a detailed comparison of different ARG
definitions. The practicality of the gARG encoding is already well recognized
in the community through various applications, such as msprime, forward-time
simulation, and the efficient computation of population genetic statistics.
\end{point}
\begin{reply}
Thank you for the kind words, we are glad you find the exposition clear.
\end{reply}

\begin{point}
However, I have reservations about categorizing this work as a standalone
``Investigation'' article. It seems to align more closely with the nature of a
review article. While the authors claim to be "proposing an alternative
mathematical formulation," this characterization might be somewhat of an
overstatement. The contribution, while valuable, appears to be more in the
realm of summarizing and clarifying existing concepts rather than introducing a
fundamentally new mathematical approach.
\end{point}
\begin{reply}
We are absolutely in agreement, and have restructured the article as a
``Perspective''.
\end{reply}

\begin{point}
The figures provided are generally helpful; however, the font size in some of
them is quite small, making them difficult to read. For instance, the node
labels in Figure 3C are impossible to read without zooming in maximally. I
suggest increasing the font size in most figures to ensure clear legibility.
\end{point}
\begin{reply}
We have modified Figure 3 to make it more legible, and will endeavour to 
adapt the figures to be legible in the final published typesetting 
(should it be accepted!).
\end{reply}
